---
title: "Four Parameters Categorical"
format: html
execute: 
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(nnet)
```

```{r}
#| cache: true
nes_92 <- nes |>
  filter(year == 1992) |>
  select(sex, pres_vote) |>
  drop_na() |>
  mutate(pres_vote = as.factor(case_when(
    pres_vote == "Democrat" ~ "Clinton",
    pres_vote == "Republican" ~ "Bush",
    pres_vote == "Third Party" ~ "Perot",
    TRUE ~ NA_character_  # fallback in case of other responses
  ))) |>
  drop_na(pres_vote)  # drop any leftover NA from unmatched categories

fit_nes <- multinom_reg(engine = "nnet") |>
  fit(pres_vote ~ sex, data = nes_92)

```

```{r}
# Load required libraries
library(tidymodels)
library(gt)

# Tidy the model output
fit_nes_table <- tidy(fit_nes, conf.int = TRUE) |>
  select(y.level, term, estimate, conf.low, conf.high) |>
  mutate(
    term = case_when(
      term == "(Intercept)" ~ "Intercept",
      term == "sexMale" ~ "Male"
    )
  ) |>
  gt() |>
  cols_label(
    y.level = "Outcome",
    term = "Term",
    estimate = "Estimate",
    conf.low = "95% CI (Lower)",
    conf.high = "95% CI (Upper)"
  ) |>
  fmt_number(columns = c(estimate, conf.low, conf.high), decimals = 3) |>
  tab_header(
    title = "Multinomial Logistic Regression Results",
    subtitle = "Modeling Voter Preference by Gender in the 1992 US Election"
  )

# Print table
fit_nes_table

```
our regression model
$$
Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_k X_k + \varepsilon
$$

$$
\begin{aligned}
\hat{\log} \left( \frac{P(\text{vote} = \text{Clinton})}{P(\text{vote} = \text{Perot})} \right) &= -0.50 - 0.80 \cdot \text{Male} \\
\hat{\log} \left( \frac{P(\text{vote} = \text{Bush})}{P(\text{vote} = \text{Perot})} \right) &= 0.20 + 0.60 \cdot \text{Male}
\end{aligned}
$$


```


Men and women may prefer different candidates, which can shape how campaigns are designed. Using data from the 1992 National Election Studies survey, we examine how voter preference varied by gender in that presidential election.A potential weakness in our model is that it assumes gender is the only driver of voting preference, potentially overlooking other influential factors such as age, race, or political ideology.We model voting preference—categorized as support for Clinton, Bush, or Perot—as a multinomial function of gender, estimating how the probability of choosing each candidate differs between men and women.
